Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-25 src/tex/ms.tex
add more macros

\begin{abstract}
We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical distribution of 
binary black hole masses and spins using the 69 confident observations in GWTC-3. We find the same features previously recovered 
with similarly flexible models in the mass distribution, namely the peaks in merger rates at \~10\msun and \~35\msun. 
We apply our method to investigate whether the spin components are indendendenty distributed with a model agnositc way, where we find that 
the spin magnitude distribution seems to be quite consistently IID, with XX\% of black hole spins below XX at XX\% credibility. We report 
slight evidence of tilt distributions that do not peak at $\cos(\theta_i) = 1$ as previous models assumed, and slight evidence that 
the components are distributed differently, in contrast to the spin magnitude distribution. While we do not find signs of a significant
zero spinning sub population we do find that the data prefer not to force the support for exactly zero spinning black holes to 0 as 
the non-singular Beta distribution and \textsc{Default} model assumes. MSpline IID:
$\cos{\theta}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][peakCosTilt]}$}
$\gamma = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][log10gammaFrac]}$}
$f_{<0} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][negFrac]}$}
MSpline Independent:
$\cos{\theta_1}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt1]}$} and $\cos{\theta_2}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt2]}$}
$\gamma_1 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and $\gamma_2 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$} 
$f_{1,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} andand $f_{2,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}
\end{abstract}

>>>>

\begin{abstract}

    Default: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelowNeg0p3]}$} 
             $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} 
             $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$}

    MSplineIID: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelowNeg0p3]}$}
                $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$} 
                $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][PeakChiEff]}$}

    MSplineIND: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelowNeg0p3]}$}
                $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelow0]}$} 
                $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][PeakChiEff]}$}

    MSplineChiEff: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelowNeg0p3]}$}
                   $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$} 
                   $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}

We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical distribution of 
binary black hole masses and spins using the 69 confident observations in GWTC-3. We find the same features previously recovered 
with similarly flexible models in the mass distribution, namely the peaks in merger rates at \~10\msun and \~35\msun. 
We apply our method to investigate whether the spin components are indendendenty distributed with a model agnositc way, where we find that 
the spin magnitude distribution seems to be quite consistently IID, with XX\% of black hole spins below XX at XX\% credibility. We report 
slight evidence of tilt distributions that do not peak at $\cos(\theta_i) = 1$ as previous models assumed, and slight evidence that 
the components are distributed differently, in contrast to the spin magnitude distribution. While we do not find signs of a significant
zero spinning sub population we do find that the data prefer not to force the support for exactly zero spinning black holes to 0 as 
the non-singular Beta distribution and \textsc{Default} model assumes. MSpline IID:
$\cos{\theta}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][peakCosTilt]}$}
$\gamma = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][log10gammaFrac]}$}
$f_{<0} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][negFrac]}$}
MSpline Independent:
$\cos{\theta_1}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt1]}$} and $\cos{\theta_2}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt2]}$}
$\gamma_1 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and $\gamma_2 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$} 
$f_{1,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} andand $f_{2,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}
\end{abstract}
